---
title: 'AlphaPipes: R package providing named magrittr-style pipe operators'
author: "Aleksander Rutkowski"
date: "`r format(Sys.Date())`"
output: github_document
always_allow_html: yes
---

The package provides "named pipes" which may complement:
the **magrittr** package pipes. The named pipes make it possible
to use all lower-case and upper-case letters as the right-hand-side
symbols/placeholders for the values piped from the left-hand-side,
while the standard **magrittr** operator `%>%`
uses only a dot.

When the package is loaded (via `library(AlphaPipes)`)
the pipe operators (`%a%` ... `%z%` and `%A%` ... `%Z%`)
are dynamically created in **AlphaPipes** namespace.
So you cannot import them via `` `%myoperator%` <- AlphaPipes::`%a%` ``.
Anyway, such an import does not seem to make sense -- namespaced operators
e.g. ``AlphaPipes::`%a%` `` would be inconvenient -- too verbose,
while *re-named* "named pipes" e.g. `%aa%` as an alias for `%a%`
would be confusing
(since symbol `a` would need to be used on the right-hand side anyway).

**AlphaPipes** needs package **clojR** which can be installed from GitHub:

`devtools::install_github('alekrutkowski/clojR')`

### Installation

`devtools::install_github('alekrutkowski/AlphaPipes')`

**AlphaPipes** needs package **clojR** which can also be installed from GitHub:

`devtools::install_github('alekrutkowski/clojR')`

### Examples

```{r}
library(AlphaPipes)
```

```{r}
# Trivial -- the same as
#  mean(1:3)
# or
#  1:3 %>% mean
1:3 %A% mean(A)
# Showing the actual usefulness -- referring to earlier values
# from the piped flow:
data.frame(xx = 1:5) %a%
    (dplyr::mutate(a, nnn = xx + 10) %b%
         dplyr::rename(b, xx2 = xx) %b%
         cbind(b, a))
# All the available "named pipes":
cat(ls(name = "package:AlphaPipes"), sep="  ")
```
